---
title: "Detecting Circular Target with Keras"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float: yes
---

# data loading ect.
```{r}
setwd('~/Documents/DataScience/R/CaseStudyR/Chapter4CircularTarget/')

# install.packages('keras')
library(keras)
library(RSQLite)
```

```{r}
con <- dbConnect(SQLite(), dbname='JRSP.db')
data<-dbReadTable(con, 'LastLookFinal')
dbDisconnect(con)

# str(data)

data<-as.matrix(data)
dimnames(data)<-NULL
```

# Normalize data
```{r}
# data[, 365]
data[, 4:363]<-normalize(data[, 4:363])

# class(data[, 365])
# summary(data)
```

# Data partition
```{r}
# training and test data
training<-data[21:100, 4:363]
test<-data[1:20, 4:363]
trainingtarget<-data[21:100,365]
testtarget<-data[1:20, 365]
```

#One hot encoding
```{r}
trainLabels<-to_categorical(trainingtarget)
testLabels<-to_categorical(testtarget)
# print(trainLabels)
```

# Create sequential model
```{r}
model<-keras_model_sequential()
model %>%
  layer_dense(units=16, activation='relu', input_shape=c(360))%>%
  layer_dense(units=4, activation='relu')%>%
  layer_dense(units=2, activation='softmax')

summary(model)
```

# Compile
```{r}
model %>%
  compile(loss='binary_crossentropy',
          optimizer='adam',
          metrics='accuracy')
```

# Fit model
```{r}
history<-model %>%
  fit(training, trainLabels, epoch=80, batch_size=32,
      validation_split=0.2)
plot(history)
```

# Evaluate model with test data
```{r}
model %>%
  evaluate(test, testLabels)
```

# Prediction & confusion matrix --test data
```{r}
prob<-model %>%
  predict_proba(test)

pred<-model %>%
  predict_classes(test)

table(Predicted=pred, Actual=testtarget)

cbind(prob, pred, testtarget)
```

# References
Useful background information about Keras
https://www.youtube.com/watch?v=hd81EH1g1bE&t=10s

Useful background information about Keras
https://keras.rstudio.com

This example is taken from: Chapter 4 Processing Robot and Sensor Log Files: Seeking a Circular Target from the book: Case Studies in Data Science with R by Deborah Nolan, University of California, Berkeley and Duncan Temple Lang, University of California, Davis. 

The complete log files can be downloaded from: http://rdatasciencecases.org/Data.html


